---
title: "Chapter 2"
output: rmarkdown::github_document
---

# Chapter 2: Small Worlds and large worlds

### Grid Approximation

1. Define the grid.
2. Compute the value of prior at each parameter value of grid.
3. Compute the likelihood at each parameter value.
4. Compute the unstandardized posterior at each parameter value, by multiplying
 the prior by the likelihood.
5. Standardize the posterior

Scales poorly with model complexity, not used.

```{r}
# define grid
p_grid <- seq(from = 0, to = 1, length.out = 20)

# define prior
prior <- rep(1, 20)

# compute likelihood at each value in grid
likelihood <- dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior
posterior <- unstd.posterior / sum(unstd.posterior)
```

```{r}
# plot
plot(p_grid, posterior, type = 'b', xlab = 'Probability of water', 
     ylab = 'Posterior probability')
mtext("20 Points")
```

### Quadratic Approximation

```{r}
library(rethinking)
globe.qa <- quap(
  alist(
    W ~ dbinom(W+L, p),
    p ~ dunif(0, 1)
  ),
  data = list(W = 6, L = 3)
)

# display summary of quadratic approximation
precis(globe.qa)
```
